A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Revise the paragraph of kinds.

The metavariables $X, Y$, and $Z$ range over the type variables.
$x, y$, and, $z$ range over the variables.
The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
$\epsilon$ is a symbol for the empty transition.

A kind is $*$ or $\Pi x:\tau.K$. Types of terms have $*$ kinds and dependent types have $\Pi$ kinds.

A type is a type variable which is declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

\red{ 
$c$ ranges over constants, 
}
In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
$\Lambda\alpha.M$ is a stage variable abstraction.
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
$\%_\alpha M$ is a primitive operator for cross-stage persistence.

>>>>

The metavariables $X, Y$, and $Z$ range over a countably infinite set of type variables.
$x, y$, and, $z$ range over a countably infinite set of variables.
The metavariables $\alpha, \beta, \text{and} \gamma$ range over the stage variables.
A transition, denoted by $A$ and $B$, is a finite sequence of stage variables.
$\epsilon$ is a symbol for the empty transition.

% Kinds

A kind is either $*$ or $\Pi x:\tau.K$.
Types of terms have kind $*$ and dependent types have $\Pi$-kinds.
For example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
\red{この段落は短いので型の段落と結合するか?}

% Types

A type is a type variable which is declared in the signature, a dependent function type,
an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

\red{ 
$c$ ranges over constants, 
}
In addition to ordinary terms in Simply Typed Lambda Calculus, there are five more forms.
$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
$\Lambda\alpha.M$ is a stage variable abstraction.
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
$\%_\alpha M$ is a primitive operator for cross-stage persistence.
